---
title: "Lab 3"
author: "Zachary Guan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

**Exercises:**  1,3 (Pgs. 90-91); 1 (Pg. 93); 2,4 (Pg. 99); 1,2 (Pg. 101); 2,3,5 (Pg. 104)

**Assigned:** Friday, February 8, 2019

**Due:** Friday, February 15, 2019 by 5:00 PM

**Submission:** Submit via an electronic document on Sakai. Must be submitted as a HTML file generated in RStudio. All assigned problems are chosen according to the textbook *R for Data Science*. You do not need R code to answer every question. If you answer without using R code, delete the code chunk. If the question requires R code, make sure you display R code. If the question requires a figure, make sure you display a figure. A lot of the questions can be answered in written response, but require R code and/or figures for understanding and explaining.

```{r, include=FALSE}
library(tidyverse)
```

# Chapter 5 (Pgs. 90-91)

##  Exercise 1
```{r}
#
ggplot(data =diamonds, aes(x=x))+
  geom_histogram(binwidth = 0.05)

ggplot(data = diamonds, mapping = aes(x=y)) +
  geom_freqpoly(binwidth = 1) 

ggplot(data =diamonds, aes(x=z))+geom_histogram(binwidth = 1) 

```
the highest peak for x(length) is ~4 mm with smaller peaks from the range of ~4-6. The y dimension(width) for diamonds is relatively fixed as the data looks unimodal around 5-10.The highest peak is around 10 for the width or y dimension of the diamonds. The depth of the diamond is also unimodal ,but the range of the data is around 3-7. 

##  Exercise 3
```{r}
#
diamonds %>% 
  filter(carat %in% c(.99,1)) %>%
  count(carat) 
```
Some diamond manufacturers may have just rounded the carat from .99 to 1 since the differnce is so small, where other companies may have not. There are only 23 observations for .99 carat ad 1.00 carat has 1558 observations so data entry could have gone wrong.


# Chapter 5 (Pg. 93)

##  Exercise 1
```{r}
#
diamonds2  <- diamonds %>% mutate(y= ifelse(y<3 | y>20, NA,y))

ggplot(data = diamonds2,mapping =aes(y)) + geom_bar(na.rm=FALSE) 

ggplot(data = diamonds2,mapping =aes(y)) + geom_histogram(bins = 1000, na.rm =FALSE) 
```
both plots had to remove the datapoints for some reason. Bar plots removed the data because the x-axis requires numerical values, not NA values. HIstograms however create bins for these values to model frequency and when a value is NA, it cannot be placed in a bin so it is removed. 
# Chapter 5 (Pg. 99)

##  Exercise 2
```{r}
#
ggplot(data= diamonds)+
  geom_boxplot(mapping = 
    aes(cut, carat))

ggplot(data= diamonds, mapping = aes(x = carat, y=price, color =cut)) + geom_smooth()
```
It is interesting to notice how in both the box plots and the geometric smooth plots that cut does not play a big influence over price. This is likely because of the covariance/effect that carat has over cut. Since carat has such a big effect, the better cut diamonds are still similar prices to lower cut diamonds that have a larger carat. 
##  Exercise 4
```{r}
#
ggplot(diamonds, aes(cut,price)) + geom_lv(aes(fill= ..LV..))
```
The geom_lv() plot provides a more detailed visual of quantiles past the Q3 upper quartile, since in large data sets box plots fail to provide an accurate prediction of the number of outliers and tail behavior beyond the lower and upper quartile become inaccurate. The lv() model lets us view quantiles past a standard boxplot and gain precise estimates of quantiles past Q1 and Q3. 

# Chapter 5 (Pg. 101)

##  Exercise 1
```{r}
#
diamonds %>% group_by(color,cut)%>%
  summarize(n = n()) %>%
  mutate(prop=n/sum(n))%>%
  ggplot(diamonds, mapping = aes(x=color,y=cut))+
  geom_tile(aes(fill = prop)) 
      


```
I tried creating proportions for each tile using dplyr to give a better visual of the distributions of cut within color
##  Exercise 2
```{r}
#
flights %>% group_by(month, dest) %>%
  summarize(arr_delay= mean(arr_delay, na.rm=TRUE))%>% 
  ggplot(mapping = aes(x=month,y=dest))+
  geom_tile(aes(fill = arr_delay)) 

```
There are too many destinations and there is alot of white space created by NA values. We could try to fix this visual by creating a better grouping or find a better way to organize certain destinations in the dataset, also removing NA values would help as the data would look more compelte .d

# Chapter 5 (Pg. 104)

##  Exercise 2
```{r}

ggplot(data= diamonds, mapping = aes(x = price, y = carat)) +
  geom_boxplot(mapping = aes(group = cut_number(price, 20))) + 
  coord_flip()
```

##  Exercise 3
```{r}

```

Based on the distribution above, there is much more variation in larger diamonds rather than smaller diamonds. This makes a lot of sense, as large diamonds can cost a lot even if their other characteristics are not very good as opposed to smaller diamonds with better characteristics. 

##  Exercise 5
```{r}
#
```
bins dont do a good job of capturing outliers unlike a scatterplot for smaller data sets. There is a strong linear association in the two variables and the scatterplot clearly shows that along with the outliers. 